---
title: "Perceptual Illusion"
subtitle: "Data Analysis"
author: "Fernando Millan Villalobos"
date: "February 2021"
output:
  html_document:
    code_folding: show
    echo: TRUE
    warning: FALSE
    message: FALSE
    highlight: pygments
    theme: paper
    df_print: kable
    toc: yes
    toc_depth: 4
    number_sections: yes
    toc_float: 
      collapsed: yes
      smooth_scroll: false
  pdf_document:
    toc: yes
  word_document:
    toc: yes
  allways_allow_html: yes
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../", output_file = "index") })
---

```{r, echo=FALSE}
# CONFIG
user_name <- "fernandomillanvillalobos" # your Git username (only needed if
# you want to deploy to GH pages)
project_name <- "2020-perceptual-illusion-master" # adapt!
package_date <- "2021-01-01" # date of the CRAN snapshot that
# the checkpoint package uses
r_version <- "4.0.3" # R-Version to use
options(Ncpus = 4) # use 4 cores for parallelized installation of packages
if (r_version != paste0(version$major, ".", version$minor)) {
  stop("ERROR: specified R version does not match currently used.")
}
```

# Notes

This report was generated on `r Sys.time()`. R version: `r paste0(version$major, ".", version$minor)` on `r version$platform`. For this report, CRAN packages as of `r package_date` were used.

## R-Script & data

The pre-processing and analysis of the data was conducted in the [R project for statistical computing](https://www.r-project.org/). The RMarkdown script used to generate this document and all the resulting data can be downloaded [under this link](http:fernandomillanvillalobs.github.io/2020-perceptual-illusion-master/). Through executing `main.Rmd`, the herein described process can be reproduced and this document can be generated. In the course of this, data from the folder `input` will be processed and results will be written to `output`. The html on-line version of the analysis can be accessed through this [link](https://fernandomillanvillalobos.github.io/2020-perceptual-illusion-master/).

## GitHub

The code for the herein described process can also be freely downloaded from [https://github.com/fernandomillanvillalobs/2020-perceptual-illusion-master](https://github.com/fernandomillanvillalobos/2020-perceptual-illusion-master).

## Data description of output files

#### `abc.csv` (Example)

| Attribute | Type    | Description |
|-----------|---------|-------------|
| a         | Numeric | ...         |
| b         | Numeric | ...         |
| c         | Numeric | ...         |

# Set up

```{r, echo=FALSE}
detach_all_packages <- function() {
  basic_packages_blank <-  c("stats",
                             "graphics",
                             "grDevices",
                             "utils",
                             "datasets",
                             "methods",
                             "base")
  basic_packages <- paste("package:", basic_packages_blank, sep = "")

  package_list <- search()[
    ifelse(unlist(gregexpr("package:", search())) == 1, TRUE, FALSE)]

  package_list <- setdiff(package_list, basic_packages)

  if (length(package_list) > 0)  for (package in package_list) {
    detach(package, character.only = TRUE, unload = TRUE)
    print(paste("package ", package, " detached", sep = ""))
  }
}

detach_all_packages()

# this allows multiple persons to use the same RMarkdown
# without adjusting the working directory by themselves all the time
source("scripts/csf.R")
path_to_wd <- csf() # if this - for some reason - does not work,
# replace with a hardcoded path, like so: "~/projects/rddj-template/analysis/"
if (is.null(path_to_wd) | !dir.exists(path_to_wd)) {
  print("WARNING: No working directory specified for current user")
} else {
  setwd(path_to_wd)
}

# suppress scientific notation
options(scipen = 999)

# unload global rstudioapi and knitr again to avoid conflicts with checkpoint
# this is only necessary if executed within RStudio
# outside of RStudio, namely in the knit.sh script, this causes RMarkdown
# rendering to fail, thus should not be executed there
if (Sys.getenv("RSTUDIO") == "1") {
  detach_all_packages()
}
```

## Define packages

```{r, echo=TRUE, message=FALSE, warning=FALSE}
# from https://mran.revolutionanalytics.com/web/packages/\
# checkpoint/vignettes/using-checkpoint-with-knitr.html
# if you don't need a package, remove it from here (commenting not sufficient)
# tidyverse: see https://blog.rstudio.org/2016/09/15/tidyverse-1-0-0/
cat("
library(rstudioapi)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble, magrittr, readxl
library(scales) # scales for ggplot2
library(jsonlite) # json
library(lintr) # code linting
library(sf) # spatial data handling
library(rmarkdown)
library(cowplot) # theme
library(extrafont) # fonts
library(waldo) # compare 
library(janitor)", # names  
file = "manifest.R")
```

## Install packages

```{r, echo=TRUE, message=FALSE, warning=FALSE}
# if checkpoint is not yet installed, install it (for people using this
# system for the first time)
if (!require(checkpoint)) {
  if (!require(devtools)) {
    install.packages("devtools", repos = "http://cran.us.r-project.org")
    require(devtools)
  }
  devtools::install_github("RevolutionAnalytics/checkpoint",
                           ref = "v0.4.10", # could be adapted later,
                           # as of now (beginning of July 2017
                           # this is the current release on CRAN)
                           repos = "http://cran.us.r-project.org")
  require(checkpoint)
}
# nolint start
if (!dir.exists("~/.checkpoint")) {
  dir.create("~/.checkpoint")
}
# nolint end
# install packages for the specified CRAN snapshot date
checkpoint(snapshotDate = package_date,
           project = path_to_wd,
           verbose = T,
           scanForPackages = T,
           use.knitr = F,
           R.version = r_version)
rm(package_date)
```

## Load packages

```{r, echo=TRUE, message=FALSE, warning=FALSE}
source("manifest.R")
unlink("manifest.R")
sessionInfo()
```

## Load additional scripts

```{r, echo=TRUE, message=FALSE, warning=FALSE}
# if you want to outsource logic to other script files, see README for 
# further information
# Load all visualizations functions as separate scripts
knitr::read_chunk("scripts/dviz.supp.R")
source("scripts/dviz.supp.R")
knitr::read_chunk("scripts/themes.R")
source("scripts/themes.R")
knitr::read_chunk("scripts/plot_grid.R")
source("scripts/plot_grid.R")
knitr::read_chunk("scripts/align_legend.R")
source("scripts/align_legend.R")
knitr::read_chunk("scripts/label_log10.R")
source("scripts/label_log10.R")
```

# Data Wrangling

Importing datasets.

```{r importing}
# Read in data file
df.j <- read.table("input/ignore/j_ds.csv", sep = ",", header = TRUE, check.names = FALSE)
df.g <- read.table("input/ignore/g_ds.csv", sep = ",", header = TRUE, check.names = FALSE)
df.v <- read.table("input/ignore/v_ds.csv", sep = ",", header = TRUE, check.names = FALSE)
df.a <- read.table("input/ignore/a_ds.csv", sep = ",", header = TRUE, check.names = FALSE)

# Cleaning variables names
df.j <- janitor::clean_names(df.j)
df.g <- janitor::clean_names(df.g)
df.v <- janitor::clean_names(df.v)
df.a <- janitor::clean_names(df.a)
```

Cleaning Julien's ds variables.

```{r cleaning_j}
# Regrouping hours_sleep bottom and top categories
df.j$hours_sleep[df.j$hours_sleep == "<3"] <- "less_than_3"
df.j$hours_sleep[df.j$hours_sleep == ">8"] <- "more_than_8"
df.j$hours_sleep[df.j$hours_sleep == "4"] <- "4-5"
df.j$hours_sleep[df.j$hours_sleep == "5"] <- "5-6"
df.j$hours_sleep[df.j$hours_sleep == "6"] <- "6-7"
df.j$hours_sleep[df.j$hours_sleep == "7"] <- "7-8"
df.j$hours_sleep[df.j$hours_sleep == "8"] <- "7-8"

# Filling empty values for circle_below and circle_above as NAs
df.j$circle_below[df.j$circle_below == ""] <- NA 
df.j$circle_above[df.j$circle_above == ""] <- NA 
```

Cleaning Gianna's ds variables.

```{r cleaning_g}
# Deleting useless column
df.g$haendigkeit <- NULL

# Renaming variables names
df.g <- df.g %>% 
  rename("age_group" = "alter",
         "education" = "ausbildung",
         "hours_sleep" = "schlaf",
         "color_blindness" = "farbenblindheit",
         "photo_exposure" = "fotos",
         "carto_gis_exposure" = "kartographie",
         "geovis_3d_exposure" = "drei_d_geovis",
         "satellite_exposure" = "satellitenbilder",
         "mask" = "maske")
```

```{r}
# Adding new variables
df.g <- transform(df.g,
                 art_light_r_w = NA, 
                 light_dir_r_s = NA,
                 photo_training = NA,
                 carto_gis_training = NA,
                 geovis_3d_training = NA,
                 satellite_training = NA,
                 circle_below = NA,
                 circle_above = NA,
                 shapes_01 = NA,
                 shapes_02 = NA,
                 shapes_03 = NA,
                 shapes_04 = NA,
                 shapes_05 = NA,
                 shapes_06 = NA,
                 shapes_07 = NA,
                 shapes_08 = NA,
                 shapes_09 = NA,
                 shapes_10 = NA)

# Reordering variables
df.g <- df.g[, names(df.j)]

# Recoding education variable
df.g$education[df.g$education == "University: Bachelor degree or equivalent"] <- "bachelor"
df.g$education[df.g$education == "University of applied sciences"] <- "bachelor" # assumption! 
df.g$education[df.g$education == "University: Master degree or equivalent"] <- "master"
df.g$education[df.g$education == "University: Doctoral degree"] <- "doctoral"
df.g$education[df.g$education == "Apprenticeship high school"] <- "high_school"
df.g$education[df.g$education == "Academic high school"] <- "high_school"

# Regrouping age_group category
df.g$age_group[df.g$age_group == "18-29" & df.g$education == "bachelor" | df.g$education == "master"] <- "20-29"
df.g$age_group[df.g$age_group == "18-29" & df.g$education == "high_school"] <- "10-19"

# Regrouping hours_sleep bottom and top categories
df.g$hours_sleep[df.g$hours_sleep == "<3"] <- "less_than_3"
df.g$hours_sleep[df.g$hours_sleep == ">8"] <- "more_than_8"
df.g$hours_sleep[df.g$hours_sleep == "3"] <- "3-4"
df.g$hours_sleep[df.g$hours_sleep == "4"] <- "4-5"
df.g$hours_sleep[df.g$hours_sleep == "5"] <- "5-6"
df.g$hours_sleep[df.g$hours_sleep == "6"] <- "6-7"
df.g$hours_sleep[df.g$hours_sleep == "7"] <- "7-8"
df.g$hours_sleep[df.g$hours_sleep == "8"] <- "7-8"

# Values to lowercase
df.g[, 16:20] <- apply(df.g[, 16:20], 2, tolower)
df.g$color_blindness <- unlist(lapply(df.g$color_blindness, tolower))

```

Cleaning Victoria's ds variables.

```{r cleaning_v}
# Adding hemisphere variable
df.v$hemisphere <- "southern"

# Reordering variables
df.v <- df.v[, names(df.j)]

# Regrouping age_group category
df.v$age_group[df.v$age_group <= "29"] <- "20-29"

# Splitting character vector from hours_sleep
df.v$hours_sleep <- unlist(strsplit(df.v$hours_sleep, " hours"))

# Recoding education variable
df.v$education <- "bachelor"

# Values to lowercase
df.v$light_dir_r_s <- unlist(lapply(df.v$light_dir_r_s, tolower))

# Filling empty values for exposure variables
df.v$photo_exposure <- ifelse(df.v$photo_exposure == " ", NA, df.v$photo_exposure)
df.v$carto_gis_exposure <- ifelse(df.v$carto_gis_exposure == " ", NA, df.v$carto_gis_exposure)
df.v$geovis_3d_exposure <- ifelse(df.v$geovis_3d_exposure == " ", NA, df.v$geovis_3d_exposure)
df.v$satellite_exposure <- ifelse(df.v$satellite_exposure == " ", NA, df.v$satellite_exposure)
```

Cleaning Amy's ds variables.

```{r cleaning_a}
# Adding hemisphere variable
df.a$hemisphere <- "southern"

# Reordering variables
df.a <- df.a[, names(df.j)]

# Regrouping age_group category
df.a$age_group[df.a$age_group <= "19"] <- "10-19"
df.a$age_group[df.a$age_group <= "29" & df.a$age_group >= 20] <- "20-29"
df.a$age_group[df.a$age_group <= "39" & df.a$age_group >= 30] <- "30-39"
df.a$age_group[df.a$age_group <= "49" & df.a$age_group >= 40] <- "40-49"
df.a$age_group[df.a$age_group <= "59" & df.a$age_group >= 50] <- "50-59"
df.a$age_group[df.a$age_group <= "69" & df.a$age_group >= 60] <- "60-69"

# Recoding education variable
df.a$education[df.a$education == "Currently registered at University/College for Bachelor degree or equivalent"] <- "bachelor"
df.a$education[df.a$education == "University/College: Bachelor degree or equivalent"] <- "bachelor"
df.a$education[df.a$education == "University/College: Honours, Masters, PhD degree or equivalent"] <- "master"
df.a$education[df.a$education == "High school diploma or equivalent ( e.g. NCS or matric )"] <- "high_school"

# Recoding hours_sleep
df.a$hours_sleep <- unlist(strsplit(df.a$hours_sleep, " hours")) # splitting characters
df.a$hours_sleep <- unlist(lapply(df.a$hours_sleep, tolower)) # values to lowercase  
df.a$hours_sleep[df.a$hours_sleep == "more than 8"] <- "more_than_8" # recoding

# Values to lowercase
df.a$art_light_r_w <- unlist(lapply(df.a$art_light_r_w, tolower))
df.a$light_dir_r_s <- unlist(lapply(df.a$light_dir_r_s, tolower))

# Filling empty values for exposure variables
df.a$photo_exposure <- ifelse(df.a$photo_exposure == " ", NA, df.a$photo_exposure)
df.a$carto_gis_exposure <- ifelse(df.a$carto_gis_exposure == " ", NA, df.a$carto_gis_exposure)
df.a$geovis_3d_exposure <- ifelse(df.a$geovis_3d_exposure == " ", NA, df.a$geovis_3d_exposure)
df.a$satellite_exposure <- ifelse(df.a$satellite_exposure == " ", NA, df.a$satellite_exposure)
```

Creating all-in-one df for analysis and viz

```{r}
df <- rbind(df.j, df.g, df.v, df.a)
```

# Linting

The code in this RMarkdown is linted with the [lintr package](https://github.com/jimhester/lintr), which is based on the [tidyverse style guide](http://style.tidyverse.org/).

```{r echo=TRUE, message=FALSE, warning=FALSE, results='hide'}
lintr::lint("main.Rmd", linters =
              lintr::with_defaults(
                commented_code_linter = NULL,
                trailing_whitespace_linter = NULL
                )
            )
# if you have additional scripts and want them to be linted too, add them here
# lintr::lint("scripts/my_script.R")
```
